Component response rate variation underlies the stability of complex systems

### 2020-03-14 notebook/SI.Rmd
Update SI to put some examples of structured networks

```{r, echo = FALSE}
source(file = "../R/Figures_3_4.R");
source(file = "R_old/sim_mat.R");
source(file = "R_old/plot_figs.R");
```

@@

- [Stability across increasing $S$](#IncrS) 
- [Stability of ecological networks](#ecological) 
    - [Competitor networks](#competition) 
    - [Mutualist networks](#mutualism) 
    - [Predator-prey networks](#pred-prey) 
- [Sensitivity of connectance (C) values](#connectance)
    - [C = 0.3](#connect3)
    - [C = 0.5](#connect5)
    - [C = 0.7](#connect7)
    - [C = 0.9](#connect9)
- [Large networks of $C = 0.05$ across $S$ and $\sigma$](#sigma)  
    - [$\sigma$ = 0.3](#sigma3)
    - [$\sigma$ = 0.4](#sigma4)
    - [$\sigma$ = 0.5](#sigma5)
    - [$\sigma$ = 0.6](#sigma6)
- [Sensitivity of distribution of $\gamma$](#gam_dist)
- [Feasibility of complex systems](#Feasibility)
- [Stability given targeted manipulation of $\gamma$ (genetic algorithm)](#ga)
- [Consistency with Gibbs et al. (2018)](#Gibbs)
- [Effects of matrix correlations](#rhos)

@@

>>>>

```{r, echo = FALSE}
source(file = "../R/Figures_3_4.R");
source(file = "R_old/sim_mat.R");
source(file = "R_old/plot_figs.R");
source(file = "../R/utilities.R")
```

@@

- [Stability across increasing $S$](#IncrS) 
- [Stability of ecological networks](#ecological) 
    - [Competitor networks](#competition) 
    - [Mutualist networks](#mutualism) 
    - [Predator-prey networks](#pred-prey) 
- [Sensitivity of connectance (C) values](#connectance)
    - [C = 0.3](#connect3)
    - [C = 0.5](#connect5)
    - [C = 0.7](#connect7)
    - [C = 0.9](#connect9)
- [Large networks of $C = 0.05$ across $S$ and $\sigma$](#sigma)  
    - [$\sigma$ = 0.3](#sigma3)
    - [$\sigma$ = 0.4](#sigma4)
    - [$\sigma$ = 0.5](#sigma5)
    - [$\sigma$ = 0.6](#sigma6)
- [Sensitivity of distribution of $\gamma$](#gam_dist)
- [Structured network construction](#structured)
- [Feasibility of complex systems](#Feasibility)
- [Stability given targeted manipulation of $\gamma$ (genetic algorithm)](#ga)
- [Consistency with Gibbs et al. (2018)](#Gibbs)
- [Effects of matrix correlations](#rhos)

@@

Structured network construction {#structured}
================================================================================

Example of a small-world network

```{r, echo = FALSE}
source("../R/small_world.R");
par(mfrow = c(1, 2), mar = c(5, 5, 1, 1));
swn <- create_swn(S = 72, K = 12, beta = 0.01);
visualise_network(swn);
swn <- create_swn(S = 72, K = 12, beta = 0.1);
visualise_network(swn);
```

Example of a scale-free network

```{r, echo = FALSE}
source("../R/scale_free.R");
sfn <- create_sfn(S = 72, m = 3);
par(mfrow = c(1, 2), mar = c(5, 5, 1, 1));
visualise_network(sfn);
dd_dat       <- sfn;
diag(dd_dat) <- 0;
deg_dist     <- apply(X = dd_dat, MARGIN = 1, FUN = sum);
hist(deg_dist, main = "", xlab = "Component interactions",
     ylab = "Frequency", cex.lab = 1.25, cex.axis = 1.25,
     col = "grey", breaks = 20);
```

### 2020-03-14 notebook/SI.tex
Update SI to put some examples of structured networks

  \begin{itemize}
  \tightlist
  \item
    \protect\hyperlink{sigma3}{\(\sigma\) = 0.3}
  \item
    \protect\hyperlink{sigma4}{\(\sigma\) = 0.4}
  \item
    \protect\hyperlink{sigma5}{\(\sigma\) = 0.5}
  \item
    \protect\hyperlink{sigma6}{\(\sigma\) = 0.6}
  \end{itemize}
\item
  \protect\hyperlink{gam_dist}{Sensitivity of distribution of
  \(\gamma\)}
\item
  \protect\hyperlink{Feasibility}{Feasibility of complex systems}
\item
  \protect\hyperlink{ga}{Stability given targeted manipulation of
  \(\gamma\) (genetic algorithm)}
\item
  \protect\hyperlink{Gibbs}{Consistency with Gibbs et al. (2018)}
\item
  \protect\hyperlink{rhos}{Effects of matrix correlations}
\end{itemize}

@@

@@

@@

{\centering \includegraphics{SI_files/figure-latex/unnamed-chunk-28-1}

@@

\includegraphics{SI_files/figure-latex/unnamed-chunk-30-1.pdf}

@@

\includegraphics{SI_files/figure-latex/unnamed-chunk-31-1.pdf}

@@

@@

\includegraphics{SI_files/figure-latex/unnamed-chunk-36-1.pdf}

@@

@@

>>>>

  \begin{itemize}
  \tightlist
  \item
    \protect\hyperlink{sigma3}{\(\sigma\) = 0.3}
  \item
    \protect\hyperlink{sigma4}{\(\sigma\) = 0.4}
  \item
    \protect\hyperlink{sigma5}{\(\sigma\) = 0.5}
  \item
    \protect\hyperlink{sigma6}{\(\sigma\) = 0.6}
  \end{itemize}
\item
  \protect\hyperlink{gam_dist}{Sensitivity of distribution of
  \(\gamma\)}
\item
  \protect\hyperlink{structured}{Structured network construction}
\item
  \protect\hyperlink{Feasibility}{Feasibility of complex systems}
\item
  \protect\hyperlink{ga}{Stability given targeted manipulation of
  \(\gamma\) (genetic algorithm)}
\item
  \protect\hyperlink{Gibbs}{Consistency with Gibbs et al. (2018)}
\item
  \protect\hyperlink{rhos}{Effects of matrix correlations}
\end{itemize}

@@

\hypertarget{structured}{\section{Structured network
construction}\label{structured}}

Example of a small-world network

\includegraphics{SI_files/figure-latex/unnamed-chunk-23-1.pdf}

Example of a scale-free network

@@

\includegraphics{SI_files/figure-latex/unnamed-chunk-28-1.pdf}

@@

{\centering \includegraphics{SI_files/figure-latex/unnamed-chunk-30-1}

@@

@@

@@

\includegraphics{SI_files/figure-latex/unnamed-chunk-34-1.pdf}

@@

@@

\includegraphics{SI_files/figure-latex/unnamed-chunk-39-1.pdf}

@@

\includegraphics{SI_files/figure-latex/unnamed-chunk-40-1.pdf}
